---
title: "Assignment Solutions"
output: html_notebook
---

**1. Use various utility functions discussed to create vectors containing these values. You need to create both (one containing 10 values and another containing 26) vectors separately.**

#### Solution:

```{r}
2^(1:10)
```

```{r}
paste0(letters,26:1)
```

___

**2. Below given is a vector containing first lines of many addresses. Extract city names from all the addresses using string functions. Hint: you can use a for loop to iterate over results of strsplit for further processing.**

```{r}
address_list = c("802/hiranandani/Mumbai",
                 "2A/kalka-Delhi",
                 "345#near adyar#Chennai",
                 "10-shyaam bazzar-Kolkata")
```


#### Solution:

```{r}
temp=gsub("-","/",address_list)
temp=gsub("#","/",temp)
l=strsplit(temp,"/")
for(i in 1:4){
print(l[[i]][3])
}
```

___

**3. Use following bit to create a vector with prime numbers in 1:47. (Prime numbers are numbers which are divisible only by themselves)**

```{r}
primes = c(2,3,5,7,11,13,17,19,23,29,31,37,41,43,47)
```

**Any number from 48 to 100 which is not divisible by any of the above listed primes is also a prime. Print those prime numbers from 48 to 100.**

#### Solution:

```{r}
for(i in 48:100){
temp=i%%primes
condition=temp==0
if(sum(condition)==0){print(i)}
}
```

___

**4. Find out, how many cars are there are in the dataset mtcars which have automatic transmission, number of forward gears higher than 3 and below average mileage. List their names and calculate average mileage from the data itself. To find out which variable in the data represent mentioned above information do ?mtcars**

#### Solution:

```{r}
?mtcars
avg=mean(mtcars$mpg)
d=mtcars[mtcars$mpg<avg & mtcars$gear>3 & mtcars$am==0,]
rownames(d)

```

**5. There is no native function in R to calculate mode for a variable. The function "mode" returns storage mode of an object, not the statistical mode that we discussed in the class. Write a function which returns modes of a character vector. Test that on the following vectors.**

```{r}
set.seed(2)
x=sample(letters[1:5],50,replace=T)
y=sample(letters[1:3],50,replace=T)
```

#### Solution:

```{r}
mymode=function(x){
t=table(x)
result=names(t)[which(t==max(t))]
return(result)
}
mymode(x)
```

```{r}
mymode=function(y){
t=table(y)
result=names(t)[which(t==max(t))]
return(result)
}
mymode(y)
```



