```{r setup, include=FALSE}

library(dplyr)
library(psych)
library(vtree)
library(ggplot2)
```


```{r}
setwd("D:/Practice/R/20210725")
```



```{r}
dataset = read.csv("diabetes.csv")
#View the dataset
# View(dataset)
print(dataset)

```



```{r}
# Lets have a look at the head of the data.
head(dataset)
```


```{r}
# Structure of dataset
str(dataset)
#glimpse(dataset)
```
```{r}
# Structure of dataset
glimpse(dataset)

```


# Details or summary of dataset
summary(dataset)
describe(dataset)


# count of columns
dim(dataset)

numCols = dim(dataset)[2]
numCols

#count missing values in each column
vector_NAs = rep(0, numCols)
vector_NAs

for (i in 1:numCols) {
  vector_NAs[i] = sum(is.na(dataset[,i]))
}

vector_NAs

# drop columns
dataset = dataset[,-c(15,16)]
print(dim(dataset))

```{r}
plot(dataset$glyhb)
```



plot(dataset$stab.glu)

plot(dataset$age)


barplot(table(dataset$gender))

ggplot(dataset, aes(x=gender)) + 
  geom_bar()

ggplot(dataset, aes(x=frame)) +
  geom_bar()


# multi variant 


```{r}
plot(dataset$glyhb, dataset$stab.glu)
```


```{r}
ggplot(dataset, aes(x=stab.glu, y=glyhb, color=diagnosis)) +
  geom_point() +
  geom_smooth(method="lm")
```




```{r}
# Picking numerical variables
dataset_numeric = dataset[,-c(7,9, 12, 18)]
View(dataset_numeric)
```



```{r}
par(mfrow=c(1,1))
# make all histogram and bar plots in one go

for (i in 2:14) {
  hist(dataset_numeric[,i], main=names(dataset_numeric)[i])
}
```



```{r}
par(mfrow=c(2,3)) # put 2 figs in a row and 3 figs in cols
# make all histogram and bar plots in one go

for (i in 2:14) {
  hist(dataset_numeric[,i], main=names(dataset_numeric)[i])
}

```
# 1st Aug 2021

```{r}
ggplot(dataset, aes(x=gender, fill=diagnosis)) + geom_bar()

```
```{r}
vtree(dataset, "gender")
```

```{r}
# Lets see gender in diagnosis
vtree(dataset, "gender diagnosis")
```
```{r}
vtree(dataset, "gender diagnosis", horiz=F)
```

```{r}
# which body frame need to focus on

vtree(dataset, "frame")
```


```{r}
vtree(dataset, "frame diagnosis")
```

```{r}
vtree(dataset, "gender frame diagnosis")
```

```{r}
# Location

vtree(dataset, "location")

```

```{r}
vtree(dataset, "location diagnosis")
```

```{r}
vtree(dataset, "location gender diagnosis")
```

```{r}
install.packages("corrplot")

```
```{r}
library(corrplot)
```
```{r}

install.packages("DataExplorer")

```

```{r}
library(DataExplorer)
```
```{r}
plot_correlation(dataset)
```
```{r}
plot_correlation(dataset_numeric)
```



